UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-15 files/paper/tex/introduction.tex

Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision 
\cite{krizhevsky2012imagenet}. Often times, these networks require large amounts of data, either labeled or paired with
ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}, paired training
data is
readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted 
by either
color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction. 
This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes 
with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots
%\starnote{Summarize the approach here. Then talk about datasets as you have done already.}
We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary 
domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
$Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining
ground truth.

>>>>

Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision 
\cite{krizhevsky2012imagenet}. Often times, these networks require large amounts of data, either labeled or paired with
ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}, paired training
data is
readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted 
by either
color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction. 
This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes 
with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots.
%\starnote{Summarize the approach here. Then talk about datasets as you have done already.}
We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary 
domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
$Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining
ground truth.
